Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-01-11 second_response_to_reviewers.tex

Most requests were on the subject of
presentation of the results as well as requests for specific pieces of further
analysis. All of these were addressed.

This latest set of comments from the reviewers are mainly of two types:

\begin{enumerate}
    \item Further minor requests for presentation modifications (specifically
        the remaining reviewer from the first round only made requests of this
        type).
    \item Questions about the suitability/impact of the work.
\end{enumerate}

As we detail below we have addressed all requests of the first type. For the
requests of the second type, from the two new reviewers we have made some modifications to the manuscript but our
main responses are to answer the questions posed by the reviewers.

@@

\section{Comments from first referee}

\begin{verbatim}
   Figures are much improved! It was a good idea to move some of them to the
Supplementary Material. I still think the title is not representative of the
work -- you should reconsider at least changing the subtitle. You are not
studying the Moran process; you are studying Prisoner's Dilemma strategies.  I
\end{verbatim}

Thank you for agreeing to review the paper again.

We have changed the subtitle to be: `an Empirical Study of strategies in the Moran
process for the Iterated Prisoner's

### 2018-01-11 main.tex
Add missing word to title!

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an Empirical Study of strategies in the Moran process for the
       Iterated Prisoner's}
\author[1]{Vincent Knight}
\author[2]{Marc Harper}
\author[1]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}

>>>>

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an Empirical Study of Strategies in the Moran process for the
       Iterated Prisoner's Dilemma}
\author[1]{Vincent Knight}
\author[2]{Marc Harper}
\author[1]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}
